Mamary Gland Development Exploratory Data Analysis

### 2017-04-05 src/QCAnalysis.Rmd
fixes to accomodate changes in upstream scripts

---
title: "Mamary Gland Development Exploratory Data Analysis"
author: "Karsten Bach"
date: '`r Sys.Date()`'
output:
  html_notebook:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: united
    highlight: tango
---
***
# Load Data and Packages
```{r, message=FALSE}
library(scran)
library(dplyr)
library(knitr)
library(ggplot2)
rnd_seed <- 300
library(Rtsne)
source("functions.R")
dataList <- readRDS("../data/Robjects/ExpressionList.rds")
m <- dataList[["counts"]]
pD <- dataList[["phenoData"]]
fD <- dataList[["featureData"]]
#relevel pD Condition to get it in logical sequence
pD$Condition <- factor(pD$Condition,levels=c("V","P","L","I"))
```
# Overview over the data

@@

***
## Save Data
```{r}
pD.add <- select(pD.filtered, barcode, sf, tSNE1, tSNE2)
fD.add <- select(fD.filtered, id, highVar)
pD <- left_join(pD,pD.add, by="barcode")
fD <- left_join(fD,fD.add, by="id")
stopifnot(identical(as.character(pD$barcode),colnames(m)))
stopifnot(identical(as.character(fD$id),rownames(m)))
out <- list()
out[[1]] <- m
out[[2]] <- pD
out[[3]] <- fD
saveRDS(out,file="../data/Robjects/ExpressionList_QC.rds")
```

>>>>

---
title: "Mamary Gland Development Exploratory Data Analysis"
author: "Karsten Bach"
date: '`r Sys.Date()`'
output:
  html_notebook:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: united
    highlight: tango
---
***
# Load Data and Packages
```{r, message=FALSE}
library(scran)
library(dplyr)
library(knitr)
library(ggplot2)
rnd_seed <- 300
library(Rtsne)
source("functions.R")
dataList <- readRDS("../data/Robjects/ExpressionList.rds")
m <- dataList[["counts"]]
pD <- dataList[["phenoData"]]
fD <- dataList[["featureData"]]
#relevel pD Condition to get it in logical sequence
# pD$Condition <- factor(pD$Condition,levels=c("V","P","L","I"))
```
# Overview over the data

@@

***
## Save Data
```{r}
pD.add <- dplyr::select(pD.filtered, barcode, sf, tSNE1, tSNE2)
fD.add <- dplyr::select(fD.filtered, id, highVar)
pD <- left_join(pD,pD.add, by="barcode")
fD <- left_join(fD,fD.add, by="id")
stopifnot(identical(as.character(pD$barcode),colnames(m)))
stopifnot(identical(as.character(fD$id),rownames(m)))
out <- list()
out[[1]] <- m
out[[2]] <- pD
out[[3]] <- fD
saveRDS(out,file="../data/Robjects/ExpressionList_QC.rds")
```
